---
title: "UC NRS Questionnaire"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, warning = FALSE, message = FALSE}
library(qualtRics)
library(dplyr) 
library(ggplot2)
library(tidyr)
library(scales)
library(stringr)
library(DT)
library(stringi)
library(igraph)
```

```{r, warning=FALSE, message=FALSE}
s <- all_surveys() %>% 
  filter(grepl("UC NRS EDMS Survey", name))

sf <- fetch_survey(s$id, verbose = FALSE, convert = FALSE) %>% 
  filter(StartDate > as.POSIXct("2022-11-01"))


questions <- survey_questions(s$id) %>% 
  mutate(number = as.numeric(gsub("Q", "", qname)))
```


```{r}
num_started <- nrow(sf)
```

### Response Status

`r num_started` questionnaires were completed as of `r Sys.time()`. 

```{r}
theme_uc <- 
  theme_bw(base_size=12,base_family="Helvetica") +
  theme(
    plot.title=element_text(size=11, face="bold",margin=margin(10,0,10,0),color="#1D244F"),
    plot.subtitle = element_text(size=10,margin=margin(0,0,10,0),color="#1D244F"),
    axis.text.x = element_text(size=8, vjust=0.5, color="#1D244F"),
    axis.text.y = element_text(size=8, color="#1D244F"),
    axis.title.x = element_text(color="#1D244F",vjust=-.5,size=10),
    axis.title.y = element_text(color="#1D244F",angle=90,vjust=.5,size=10),
    panel.background=element_rect(fill="white"),
    axis.line = element_line(color="#1D244F"),
    panel.grid.major = element_line(colour = "gray", size = 0.01), 
    panel.grid.minor = element_line(colour = "gray", size = 0.04),
  )
```


### Primary Reserve and Activities

```{r, fig.width=12, fig.height=8}
q1 <- sf %>% 
  select("Q1") %>% 
  mutate(Q1 = as.character(Q1)) %>% 
  group_by(Q1) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()

q1$Q1 <- factor(q1$Q1, levels = rev(q1$Q1))

ggplot(q1, aes(x = Q1, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), hjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "What primary reserve do you interact with?") +
  theme_uc +
  coord_flip()

```


```{r}
q2 <- sf %>% 
  select(starts_with("Q2")) %>% 
  unite(all_ans, sep = ", ", na.rm = TRUE) %>% 
  filter(all_ans != "")

```

```{r}
q3 <- sf %>% 
  select("Q3") %>% 
  mutate(Q3 = as.character(Q3)) %>% 
  group_by(Q3) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()

q3$Q3 <- factor(q3$Q3, levels = q3$Q3)

ggplot(q3, aes(x = Q3, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "What is your primary activity at UC NRS Reserves?") +
  theme_uc

```

```{r}
q3_t <- sf %>% 
  select(starts_with("Q3_5"))  %>% 
  drop_na() %>% 
  mutate(Q3_5_TEXT= tolower(Q3_5_TEXT)) %>% 
  mutate(Q3_5_TEXT = trimws(Q3_5_TEXT, which = "both")) %>% 
  group_by(Q3_5_TEXT) %>% 
  summarise(n = n()) %>% 
  filter(Q3_5_TEXT != "") %>% 
  arrange(-n) %>% 
  rename(`Other (please indicate)` = Q3_5_TEXT)
  


datatable(q3_t, )
```

### Data Collection

```{r}
q4 <- sf %>% 
  select("Q4") %>% 
  mutate(Q4 = as.character(Q4)) %>% 
  group_by(Q4) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()

q4$Q4 <- factor(q4$Q4, levels = q4$Q4)

ggplot(q4, aes(x = Q4, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "Do you collect data at UC NRS Reserve sites?") +
  theme_uc

```


```{r, fig.width=12, fig.height=8}
q5 <- sf %>% 
  select(starts_with("Q5")) %>% 
  pivot_longer(cols = starts_with("Q5"), names_to = "t", values_to = "Q5") %>% 
  mutate(Q5 = as.character(Q5)) %>% 
  group_by(Q5) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()

q5$Q5 <- factor(q5$Q5, levels = rev(q5$Q5))

ggplot(q5, aes(x = Q5, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), hjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "At which Reserve sites do you collect data?") +
  theme_uc +
  coord_flip()
```


```{r}
q6 <- sf %>% 
  select("Q6") %>% 
  mutate(Q6 = as.character(Q6)) %>% 
  group_by(Q6) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()

q6$Q6 <- factor(q6$Q6, levels = q6$Q6)

ggplot(q6, aes(x = Q6, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "How do you primarily use data you collect at NRS Reserve sites?") +
  theme_uc
```

```{r}
q6_t <- sf %>% 
  select(starts_with("Q6_4_TEXT"))  %>% 
  drop_na() %>% 
  mutate(Q6_4_TEXT= tolower(Q6_4_TEXT)) %>% 
  mutate(Q6_4_TEXT = trimws(Q6_4_TEXT, which = "both")) %>% 
  group_by(Q6_4_TEXT) %>% 
  summarise(n = n()) %>% 
  filter(Q6_4_TEXT != "") %>% 
  arrange(-n) %>% 
  rename(`Other (please indicate)` = Q6_4_TEXT)
  


datatable(q6_t, )
```


```{r}
q7 <- sf %>% 
  select(starts_with("Q7")) %>% 
  mutate(Q7 = as.character(Q7)) %>% 
  group_by(Q7) %>% 
  summarise(n = n()) %>% 
  arrange(n) %>% 
  drop_na()

# set the question responses as a factor so you can order it in the plot
q7$Q7 <- factor(q7$Q7, levels = c("< 1 GB",
                                          "1-10 GB",
                                          "10-100 GB",
                                          "100 GB - 1 TB",
                                          "> 1 TB"))

ggplot(q7, aes(x = Q7, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "How much data have you collected, in total?") +
  theme_uc
```


```{r, fig.width=12,  fig.height=8}
q8 <- sf %>% 
  select(starts_with("Q8")) %>% 
  pivot_longer(cols = starts_with("Q8"), names_to = "t", values_to = "Q8") %>% 
  mutate(Q8 = as.character(Q8)) %>% 
  group_by(Q8) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()

q8$Q8 <- factor(q8$Q8, levels = rev(q8$Q8))

ggplot(q8, aes(x = Q8, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), hjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "In what disciplines do your data fall?") +
  theme_uc +
  coord_flip()
```


```{r, fig.width=10}
q9 <- sf %>% 
  select(Q9_1:Q9_8) %>% 
  pivot_longer(cols = starts_with("Q9"), names_to = "t", values_to = "Q9") %>% 
  mutate(Q9 = as.character(Q9)) %>% 
  group_by(Q9) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()  %>% 
  mutate(Q9 = gsub("\\s*\\([^\\)]+\\)","", Q9))

q9$Q9 <- factor(q9$Q9, levels = q9$Q9)

ggplot(q9, aes(x = Q9, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "What methods do you use?") +
  theme_uc
```

```{r}
q9_t <- sf %>% 
  select(starts_with("Q9_8_TEXT")) %>% 
  drop_na() %>% 
  mutate(Q9_8_TEXT= tolower(Q9_8_TEXT)) %>% 
  mutate(Q9_8_TEXT = trimws(Q9_8_TEXT, which = "both")) %>% 
  group_by(Q9_8_TEXT) %>% 
  summarise(n = n()) %>% 
  filter(Q9_8_TEXT != "") %>% 
  arrange(-n) %>% 
  rename(`Other (please indicate)` = Q9_8_TEXT)
  


datatable(q9_t, )
```

### Data Sharing

**NOTE: The first 75 respondants were not able to answer this question due to a survey update issue**

```{r}
q10 <- sf %>% 
  select(starts_with("Q10")) %>% 
  mutate(Q10 = as.character(Q10)) %>% 
  group_by(Q10) %>% 
  summarise(n = n()) %>% 
  arrange(n) %>% 
  drop_na()

# set the question responses as a factor so you can order it in the plot
q10$Q10 <- factor(q10$Q10, levels = rev(c("None",
                                          "< 25%",
                                          "25 - 50%",
                                          "50 - 75%",
                                          "> 75%")))

ggplot(q10, aes(x = Q10, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "How much data have you shared with a DOI?") +
  theme_uc
```


```{r, fig.width=8}
q11 <- sf %>% 
  select(Q11_1:Q11_8) %>% 
  pivot_longer(cols = starts_with("Q11"), names_to = "t", values_to = "Q11") %>% 
  mutate(Q11 = as.character(Q11)) %>% 
  group_by(Q11) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na() %>% 
  mutate(Q11 = gsub("\\s*\\([^\\)]+\\)","", Q11))

q11$Q11 <- factor(q11$Q11, levels = q11$Q11)

ggplot(q11, aes(x = Q11, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "On what platforms do you share your data?") +
  theme_uc

```


```{r}
q11_t <- sf %>% 
  select(starts_with("Q11_8_T")) %>% 
  drop_na() %>% 
  mutate(Q11_8_TEXT= tolower(Q11_8_TEXT)) %>% 
  mutate(Q11_8_TEXT = trimws(Q11_8_TEXT, which = "both")) %>% 
  group_by(Q11_8_TEXT) %>% 
  summarise(n = n()) %>% 
  filter(Q11_8_TEXT != "") %>% 
  arrange(-n) %>% 
  rename(`Other (please indicate)` = Q11_8_TEXT)
  


datatable(q11_t, )
```


```{r}
q12 <- sf %>% 
    select(Q12) %>% 
    drop_na() %>% 
    mutate(Q12= tolower(Q12)) %>% 
    mutate(Q12 = gsub("http://www.", "", Q12)) %>% 
    mutate(Q12 = gsub("http://", "", Q12)) %>% 
    mutate(Q12 = gsub("https://www.", "", Q12)) %>% 
    mutate(Q12 = gsub("https://", "", Q12)) %>% 
    mutate(Q12 = gsub(".com | .org", "", Q12)) %>%  
    mutate(Q12 = gsub("n/a", "", Q12)) %>% 
    mutate(Q12 = gsub("[/;.]", ",", Q12)) %>% 
    mutate(Q12 = gsub("and", ",", Q12)) %>% 
    mutate(Q12 = gsub("california data exchange center", "ceden", Q12))

sp <- stri_split_fixed(q12$Q12, pattern = ",", simplify = TRUE) %>% 
    as.data.frame() %>% 
    pivot_longer(cols = everything(), names_to = "t", values_to = "platform") %>% 
    mutate(platform = gsub("and", "", platform)) %>% 
    mutate(platform = gsub("[^[:alnum:] ]", "", platform)) %>% 
    mutate(platform = trimws(platform, which = "both")) %>% 
    mutate(platform_ceden = str_extract(platform, "ceden")) %>% 
    mutate(platform = ifelse(!is.na(platform_ceden), platform_ceden, platform)) %>% 
    group_by(platform) %>% 
    summarise(n = n()) %>% 
    filter(platform != "") %>% 
    arrange(-n) %>% 
    filter(!(platform %in% c("org", "data", "gov", "www", "ca"))) %>% 
    rename(`What specific platforms do you share your data on?` = platform)



datatable(sp)
```

### Data Re-use

```{r}
q13 <- sf %>% 
  select("Q13") %>% 
  mutate(Q13 = as.character(Q13)) %>% 
  group_by(Q13) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()

q13$Q13 <- factor(q13$Q13, levels = q13$Q13)

ggplot(q13, aes(x = Q13, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "Do you use data collected by others?") +
  theme_uc
```

```{r, fig.width=10}
q14 <- sf %>% 
  select(Q14_1:Q14_6) %>% 
  pivot_longer(cols = starts_with("Q14"), names_to = "t", values_to = "Q14") %>% 
  mutate(Q14 = as.character(Q14)) %>% 
  group_by(Q14) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na() %>% 
  mutate(Q14 = gsub("\\s*\\([^\\)]+\\)","", Q14))

q14$Q14 <- factor(q14$Q14, levels = q14$Q14)

ggplot(q14, aes(x = Q14, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  scale_x_discrete(labels = label_wrap(30)) +
  labs(x = "", y = "Number of responses", title = "How did you access those data?") +
  theme_uc

```


```{r}
q14_t <- sf %>% 
  select(starts_with("Q14_6_TEXT")) %>% 
  drop_na() %>% 
  mutate(Q14_6_TEXT= tolower(Q14_6_TEXT)) %>% 
  mutate(Q14_6_TEXT = trimws(Q14_6_TEXT, which = "both")) %>% 
  group_by(Q14_6_TEXT) %>% 
  summarise(n = n()) %>% 
  filter(Q14_6_TEXT != "") %>% 
  arrange(-n) %>% 
  rename(`Other (please indicate)` = Q14_6_TEXT)
  


datatable(q14_t, )
```


```{r}
q15 <- sf %>% 
  select("Q15") %>% 
  mutate(Q15 = as.character(Q15)) %>% 
  group_by(Q15) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()

q15$Q15 <- factor(q15$Q15, levels = q15$Q15)

ggplot(q15, aes(x = Q15, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "How do you primarily use data collected by others?") +
  theme_uc

```


```{r}
q15_t <- sf %>% 
  select(starts_with("Q15_4_TEXT"))  %>% 
  drop_na() %>% 
  mutate(Q15_4_TEXT= tolower(Q15_4_TEXT)) %>% 
  mutate(Q15_4_TEXT = trimws(Q15_4_TEXT, which = "both")) %>% 
  group_by(Q15_4_TEXT) %>% 
  summarise(n = n()) %>% 
  filter(Q15_4_TEXT != "") %>% 
  arrange(-n) %>% 
  rename(`Other (please indicate)` = Q15_4_TEXT)
  


datatable(q15_t, )
```


```{r}
q16 <- sf %>% 
  select(Q16) %>% 
  drop_na() %>% 
  mutate(Q16= tolower(Q16)) %>% 
  filter(!(Q16 %in% c("no", "n/a", "none", "na", "not right now.", "not currently", "not that i can think of"))) %>% 
  rename(`Are there data you wish you had access to?` = Q16)

datatable(q16)
```

```{r, fig.width=10}
q17 <- sf %>% 
  select(Q17_1:Q17_8) %>% 
  pivot_longer(cols = starts_with("Q17"), names_to = "t", values_to = "Q17") %>% 
  mutate(Q17 = as.character(Q17)) %>% 
  group_by(Q17) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na() %>% 
  mutate(Q17 = gsub("\\s*\\([^\\)]+\\)","", Q17))

q17$Q17 <- factor(q17$Q17, levels = q17$Q17)

ggplot(q17, aes(x = Q17, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25) +
  scale_x_discrete(labels = label_wrap(20)) +
  labs(x = "", y = "Number of responses", title = "What types of data should the NRS prioritize in making available?") +
  theme_uc

```


```{r}
q17_t <- sf %>% 
  select(starts_with("Q17_8_TEXT"))  %>% 
  drop_na() %>% 
  mutate(Q17_8_TEXT= tolower(Q17_8_TEXT)) %>% 
  mutate(Q17_8_TEXT = trimws(Q17_8_TEXT, which = "both")) %>% 
  group_by(Q17_8_TEXT) %>% 
  summarise(n = n()) %>% 
  filter(Q17_8_TEXT != "") %>% 
  arrange(-n) %>% 
  rename(`Other (please indicate)` = Q17_8_TEXT)
  


datatable(q17_t, )
```

### Research Station Amenities

For the following question, scores for each option are calculated by taking the sum of the rank-normalized number of votes. Votes with rank values higher than 5 are discarded.  

$$ Score = \sum_{0}^r \frac{n_1}{1}+\frac{n_2}{2}+\frac{n_3}{3} + \frac{n_4}{4} + \frac{n_5}{5} $$

Where $n_1$ is the number of votes with a rank of 1, $n_2$ is the number of votes with a rank of 2, etc. Scores are then summed over all responses ($r$).


```{r, fig.width=12}
q18 <- sf %>% 
  select(starts_with("Q18"))

  
answers <- lapply(q18, attr, "label") %>% 
  unlist() %>% 
  unname() %>% 
  stringr::str_extract("- .*$") %>% 
    gsub("- ", "", .)

names(q18) <- answers  

q18 <- 
  pivot_longer(q18, cols = everything(), names_to = "Item", values_to = "Rank")

df <- list()
for (i in 1:5){
  df[[i]] <- q18 %>% 
    filter(Rank == i) %>% 
    group_by(Item, Rank) %>% 
    summarise(n = n(), .groups = "drop")
}


df_all <- do.call(rbind, df) %>% 
  mutate(norm_vote = n/Rank) %>% 
  group_by(Item) %>% 
  summarise(norm_rank = sum(norm_vote), .groups = "drop") %>% 
  arrange(norm_rank)

df_all$Item <- factor(df_all$Item, levels = df_all$Item)



ggplot(df_all, aes(x = Item, y = norm_rank))+
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=round(norm_rank)), position=position_dodge(width=0.9), hjust=-0.25) +
  #scale_x_discrete(labels = label_wrap(30)) +
  labs(x = "", y = "Total score", title = "What currently offered research station amenities or services do you think\nare the most important to facilitating your work? (Rank from 1 to 5)") +
  theme_uc +
  coord_flip()
```


```{r, fig.width=8}
q19 <- sf %>% 
  select(Q19_1:Q19_10) %>% 
  pivot_longer(cols = starts_with("Q19"), names_to = "t", values_to = "Q19") %>% 
  mutate(Q19 = as.character(Q19)) %>% 
  group_by(Q19) %>% 
  summarise(n = n()) %>% 
  arrange(-n) %>% 
  drop_na()

q19$Q19 <- factor(q19$Q19, levels = rev(q19$Q19))

ggplot(q19, aes(x = Q19, y = n)) +
  geom_col(fill = "#2C5786") +
  geom_text(aes(label=n), position=position_dodge(width=0.9), hjust=-0.25) +
  scale_x_discrete(labels = label_wrap(30)) +
  labs(x = "", y = "Number of responses", title = "Where should further investments be made by the UC NRS to enable key\nadvances in information management and data sharing?") +
  theme_uc +
  coord_flip()

```


```{r}
q19_t <- sf %>% 
  select(starts_with("Q19_10_TEXT"))  %>% 
  drop_na() %>% 
  mutate(Q19_10_TEXT= tolower(Q19_10_TEXT)) %>% 
  mutate(Q19_10_TEXT = trimws(Q19_10_TEXT, which = "both")) %>% 
  group_by(Q19_10_TEXT) %>% 
  summarise(n = n()) %>% 
  filter(Q19_10_TEXT != "") %>% 
  arrange(-n) %>% 
  rename(`Other (please indicate)` = Q19_10_TEXT)
  


datatable(q19_t, )
```


```{r}
q21 <- sf %>% 
  select(Q21) %>% 
  drop_na() %>% 
  rename(`Additional comments` = Q21)

datatable(q21)
```


### Network of primary reserve (nodes) and other reserves (edges)

Nodes are sized by the number of respondents who indicated that reserve as their primary reserve. Edges are sized (by thickness) according to the number of times each node is connected. So, thicker lines mean more respondents use the same primary and other reserve pair.


```{r}
prim_reserve <- sf %>% 
  select(Q1) %>% 
  rename(primary= Q1)


other_reserves <- sf %>% 
  select(starts_with("Q2_"))

  
answers <- lapply(other_reserves, attr, "label") %>% 
  unlist() %>% 
  unname() %>% 
  stringr::str_extract("- .*$") %>% 
    gsub("- ", "", .)

names(other_reserves) <- answers  

other_reserves$primary <- prim_reserve$primary

other_reserves_long <- other_reserves %>% 
  pivot_longer(-primary, names_to = "reserve", values_to = "reserve2", values_drop_na = TRUE) %>% 
  select(-reserve2) %>% 
  filter(primary != "Multiple reserves equally") %>% 
  drop_na()
  
q1t <- q1 %>% 
  mutate(Q1 = as.character(Q1)) %>% 
  rename(primary = Q1) %>% 
  filter(primary != "Multiple reserves equally") 


i <- which(!(answers%in% q1t$primary))

q_add <- data.frame(primary = answers[i], n = 0)

qtot <- rbind(q1t, q_add)


attr(other_reserves_long$primary, "label") <- NULL

wrap_strings <- function(vector_of_strings,width){
  as.character(sapply(vector_of_strings, FUN=function(x){
                        paste(strwrap(x, width=width), collapse="\n")
                        }))
}

other_reserves_long$primary <- wrap_strings(other_reserves_long$primary, 15)
other_reserves_long$reserve <- wrap_strings(other_reserves_long$reserve, 15)

qtot$primary <- wrap_strings(qtot$primary, 15)

```


```{r, fig.width=15, fig.height=15}
rnet <- graph_from_data_frame(other_reserves_long, vertices = qtot)

kamadaLayout <- layout.kamada.kawai(rnet)
E(rnet)$weight <- 1 
rnet <- simplify(rnet, edge.attr.comb=list(weight="sum"))

V(rnet)$size = V(rnet)$n/1.5
```


```{r}
plot.igraph2=function (x, axes = FALSE, add = FALSE, xlim = c(-1, 1), ylim = c(-1, 
    1), mark.groups = list(), mark.shape = 1/2, mark.col = rainbow(length(mark.groups), 
    alpha = 0.3), mark.border = rainbow(length(mark.groups), 
    alpha = 1), mark.expand = 15, ...) 
{
    graph <- x
    if (!is_igraph(graph)) {
        stop("Not a graph object")
    }
    params <- i.parse.plot.params(graph, list(...))
    vertex.size <- 1/200 * params("vertex", "size")
    label.family <- params("vertex", "label.family")
    label.font <- params("vertex", "label.font")
    label.cex <- params("vertex", "label.cex")
    label.degree <- params("vertex", "label.degree")
    label.color <- params("vertex", "label.color")
    label.dist <- params("vertex", "label.dist")
    labels <- params("vertex", "label")
    shape <- igraph.check.shapes(params("vertex", "shape"))
    edge.color <- params("edge", "color")
    edge.width <- params("edge", "width")
    edge.lty <- params("edge", "lty")
    arrow.mode <- params("edge", "arrow.mode")
    edge.labels <- params("edge", "label")
    loop.angle <- params("edge", "loop.angle")
    edge.label.font <- params("edge", "label.font")
    edge.label.family <- params("edge", "label.family")
    edge.label.cex <- params("edge", "label.cex")
    edge.label.color <- params("edge", "label.color")
    elab.x <- params("edge", "label.x")
    elab.y <- params("edge", "label.y")
    arrow.size <- params("edge", "arrow.size")
    arrow.width <- params("edge", "arrow.width")
    curved <- params("edge", "curved")
    if (is.function(curved)) {
        curved <- curved(graph)
    }
    layout <- params("plot", "layout")
    margin <- params("plot", "margin")
    margin <- rep(margin, length = 4)
    rescale <- params("plot", "rescale")
    asp <- params("plot", "asp")
    frame <- params("plot", "frame")
    main <- params("plot", "main")
    sub <- params("plot", "sub")
    xlab <- params("plot", "xlab")
    ylab <- params("plot", "ylab")
    palette <- params("plot", "palette")
    if (!is.null(palette)) {
        old_palette <- palette(palette)
        on.exit(palette(old_palette), add = TRUE)
    }
    arrow.mode <- i.get.arrow.mode(graph, arrow.mode)
    maxv <- max(vertex.size)
    if (rescale) {
        layout <- norm_coords(layout, -1, 1, -1, 1)
        xlim <- c(xlim[1] - margin[2] - maxv, xlim[2] + margin[4] + 
            maxv)
        ylim <- c(ylim[1] - margin[1] - maxv, ylim[2] + margin[3] + 
            maxv)
    }
    if (!add) {
        plot(0, 0, type = "n", xlab = xlab, ylab = ylab, xlim = xlim, 
            ylim = ylim, axes = axes, frame = frame, asp = asp, 
            main = main, sub = sub)
    }
    if (!is.list(mark.groups) && is.numeric(mark.groups)) {
        mark.groups <- list(mark.groups)
    }
    mark.shape <- rep(mark.shape, length = length(mark.groups))
    mark.border <- rep(mark.border, length = length(mark.groups))
    mark.col <- rep(mark.col, length = length(mark.groups))
    mark.expand <- rep(mark.expand, length = length(mark.groups))
    for (g in seq_along(mark.groups)) {
        v <- V(graph)[mark.groups[[g]]]
        if (length(vertex.size) == 1) {
            vs <- vertex.size
        }
        else {
            vs <- rep(vertex.size, length = vcount(graph))[v]
        }
        igraph.polygon(layout[v, , drop = FALSE], vertex.size = vs, 
            expand.by = mark.expand[g]/200, shape = mark.shape[g], 
            col = mark.col[g], border = mark.border[g])
    }
    el <- as_edgelist(graph, names = FALSE)
    loops.e <- which(el[, 1] == el[, 2])
    nonloops.e <- which(el[, 1] != el[, 2])
    loops.v <- el[, 1][loops.e]
    loop.labels <- edge.labels[loops.e]
    loop.labx <- if (is.null(elab.x)) {
        rep(NA, length(loops.e))
    }
    else {
        elab.x[loops.e]
    }
    loop.laby <- if (is.null(elab.y)) {
        rep(NA, length(loops.e))
    }
    else {
        elab.y[loops.e]
    }
    edge.labels <- edge.labels[nonloops.e]
    elab.x <- if (is.null(elab.x)) 
        NULL
    else elab.x[nonloops.e]
    elab.y <- if (is.null(elab.y)) 
        NULL
    else elab.y[nonloops.e]
    el <- el[nonloops.e, , drop = FALSE]
    edge.coords <- matrix(0, nrow = nrow(el), ncol = 4)
    edge.coords[, 1] <- layout[, 1][el[, 1]]
    edge.coords[, 2] <- layout[, 2][el[, 1]]
    edge.coords[, 3] <- layout[, 1][el[, 2]]
    edge.coords[, 4] <- layout[, 2][el[, 2]]
    if (length(unique(shape)) == 1) {
        ec <- .igraph.shapes[[shape[1]]]$clip(edge.coords, el, 
            params = params, end = "both")
    }
    else {
        shape <- rep(shape, length = vcount(graph))
        ec <- edge.coords
        ec[, 1:2] <- t(sapply(seq(length = nrow(el)), function(x) {
            .igraph.shapes[[shape[el[x, 1]]]]$clip(edge.coords[x, 
                , drop = FALSE], el[x, , drop = FALSE], params = params, 
                end = "from")
        }))
        ec[, 3:4] <- t(sapply(seq(length = nrow(el)), function(x) {
            .igraph.shapes[[shape[el[x, 2]]]]$clip(edge.coords[x, 
                , drop = FALSE], el[x, , drop = FALSE], params = params, 
                end = "to")
        }))
    }
    x0 <- ec[, 1]
    y0 <- ec[, 2]
    x1 <- ec[, 3]
    y1 <- ec[, 4]
    if (length(loops.e) > 0) {
        ec <- edge.color
        if (length(ec) > 1) {
            ec <- ec[loops.e]
        }
        point.on.cubic.bezier <- function(cp, t) {
            c <- 3 * (cp[2, ] - cp[1, ])
            b <- 3 * (cp[3, ] - cp[2, ]) - c
            a <- cp[4, ] - cp[1, ] - c - b
            t2 <- t * t
            t3 <- t * t * t
            a * t3 + b * t2 + c * t + cp[1, ]
        }
        compute.bezier <- function(cp, points) {
            dt <- seq(0, 1, by = 1/(points - 1))
            sapply(dt, function(t) point.on.cubic.bezier(cp, 
                t))
        }
        plot.bezier <- function(cp, points, color, width, arr, 
            lty, arrow.size, arr.w) {
            p <- compute.bezier(cp, points)
            polygon(p[1, ], p[2, ], border = color, lwd = width, 
                lty = lty)
            if (arr == 1 || arr == 3) {
                igraph.Arrows(p[1, ncol(p) - 1], p[2, ncol(p) - 
                  1], p[1, ncol(p)], p[2, ncol(p)], sh.col = color, 
                  h.col = color, size = arrow.size, sh.lwd = width, 
                  h.lwd = width, open = FALSE, code = 2, width = arr.w)
            }
            if (arr == 2 || arr == 3) {
                igraph.Arrows(p[1, 2], p[2, 2], p[1, 1], p[2, 
                  1], sh.col = color, h.col = color, size = arrow.size, 
                  sh.lwd = width, h.lwd = width, open = FALSE, 
                  code = 2, width = arr.w)
            }
        }
        loop <- function(x0, y0, cx = x0, cy = y0, color, angle = 0, 
            label = NA, width = 1, arr = 2, lty = 1, arrow.size = arrow.size, 
            arr.w = arr.w, lab.x, lab.y) {
            rad <- angle
            center <- c(cx, cy)
            cp <- matrix(c(x0, y0, x0 + 0.4, y0 + 0.2, x0 + 0.4, 
                y0 - 0.2, x0, y0), ncol = 2, byrow = TRUE)
            phi <- atan2(cp[, 2] - center[2], cp[, 1] - center[1])
            r <- sqrt((cp[, 1] - center[1])^2 + (cp[, 2] - center[2])^2)
            phi <- phi + rad
            cp[, 1] <- cx + r * cos(phi)
            cp[, 2] <- cy + r * sin(phi)
            plot.bezier(cp, 50, color, width, arr = arr, lty = lty, 
                arrow.size = arrow.size, arr.w = arr.w)
            if (is.language(label) || !is.na(label)) {
                lx <- x0 + 0.3
                ly <- y0
                phi <- atan2(ly - center[2], lx - center[1])
                r <- sqrt((lx - center[1])^2 + (ly - center[2])^2)
                phi <- phi + rad
                lx <- cx + r * cos(phi)
                ly <- cy + r * sin(phi)
                if (!is.na(lab.x)) {
                  lx <- lab.x
                }
                if (!is.na(lab.y)) {
                  ly <- lab.y
                }
                text(lx, ly, label, col = edge.label.color, font = edge.label.font, 
                  family = edge.label.family, cex = edge.label.cex)
            }
        }
        ec <- edge.color
        if (length(ec) > 1) {
            ec <- ec[loops.e]
        }
        vs <- vertex.size
        if (length(vertex.size) > 1) {
            vs <- vs[loops.v]
        }
        ew <- edge.width
        if (length(edge.width) > 1) {
            ew <- ew[loops.e]
        }
        la <- loop.angle
        if (length(loop.angle) > 1) {
            la <- la[loops.e]
        }
        lty <- edge.lty
        if (length(edge.lty) > 1) {
            lty <- lty[loops.e]
        }
        arr <- arrow.mode
        if (length(arrow.mode) > 1) {
            arr <- arrow.mode[loops.e]
        }
        asize <- arrow.size
        if (length(arrow.size) > 1) {
            asize <- arrow.size[loops.e]
        }
        xx0 <- layout[loops.v, 1] + cos(la) * vs
        yy0 <- layout[loops.v, 2] - sin(la) * vs
        mapply(loop, xx0, yy0, color = ec, angle = -la, label = loop.labels, 
            lty = lty, width = ew, arr = arr, arrow.size = asize, 
            arr.w = arrow.width, lab.x = loop.labx, lab.y = loop.laby)
    }
    if (length(x0) != 0) {
        if (length(edge.color) > 1) {
            edge.color <- edge.color[nonloops.e]
        }
        if (length(edge.width) > 1) {
            edge.width <- edge.width[nonloops.e]
        }
        if (length(edge.lty) > 1) {
            edge.lty <- edge.lty[nonloops.e]
        }
        if (length(arrow.mode) > 1) {
            arrow.mode <- arrow.mode[nonloops.e]
        }
        if (length(arrow.size) > 1) {
            arrow.size <- arrow.size[nonloops.e]
			#modify here for multple arrow sizes - will pad out vector inside arrow function
			arrow.size = arrow.size[!is.na(arrow.size)]
        }
        if (length(curved) > 1) {
            curved <- curved[nonloops.e]
        }
        if (length(unique(arrow.mode)) == 1) {
            lc <- igraph.Arrows2(x0, y0, x1, y1, h.col = edge.color, 
                sh.col = edge.color, sh.lwd = edge.width, h.lwd = 1, 
                open = FALSE, code = arrow.mode[1], sh.lty = edge.lty, 
                h.lty = 1, size = arrow.size, width = arrow.width, 
                curved = curved)
            lc.x <- lc$lab.x
            lc.y <- lc$lab.y
        }
        else {
            curved <- rep(curved, length = ecount(graph))[nonloops.e]
            lc.x <- lc.y <- numeric(length(curved))
            for (code in 0:3) {
                valid <- arrow.mode == code
                if (!any(valid)) {
                  next
                }
                ec <- edge.color
                if (length(ec) > 1) {
                  ec <- ec[valid]
                }
                ew <- edge.width
                if (length(ew) > 1) {
                  ew <- ew[valid]
                }
                el <- edge.lty
                if (length(el) > 1) {
                  el <- el[valid]
                }
                lc <- igraph.Arrows(x0[valid], y0[valid], x1[valid], 
                  y1[valid], code = code, sh.col = ec, h.col = ec, 
                  sh.lwd = ew, h.lwd = 1, h.lty = 1, sh.lty = el, 
                  open = FALSE, size = arrow.size, width = arrow.width, 
                  curved = curved[valid])
                lc.x[valid] <- lc$lab.x
                lc.y[valid] <- lc$lab.y
            }
        }
        if (!is.null(elab.x)) {
            lc.x <- ifelse(is.na(elab.x), lc.x, elab.x)
        }
        if (!is.null(elab.y)) {
            lc.y <- ifelse(is.na(elab.y), lc.y, elab.y)
        }
        text(lc.x, lc.y, labels = edge.labels, col = edge.label.color, 
            family = edge.label.family, font = edge.label.font, 
            cex = edge.label.cex)
    }
    rm(x0, y0, x1, y1)
    if (length(unique(shape)) == 1) {
        .igraph.shapes[[shape[1]]]$plot(layout, params = params)
    }
    else {
        sapply(seq(length = vcount(graph)), function(x) {
            .igraph.shapes[[shape[x]]]$plot(layout[x, , drop = FALSE], 
                v = x, params = params)
        })
    }
    par(xpd = TRUE)
    x <- layout[, 1] + label.dist * cos(-label.degree) * (vertex.size + 
        6 * 8 * log10(2))/200
    y <- layout[, 2] + label.dist * sin(-label.degree) * (vertex.size + 
        6 * 8 * log10(2))/200
    if (length(label.family) == 1) {
        text(x, y, labels = labels, col = label.color, family = label.family, 
            font = label.font, cex = label.cex)
    }
    else {
        if1 <- function(vect, idx) if (length(vect) == 1) 
            vect
        else vect[idx]
        sapply(seq_len(vcount(graph)), function(v) {
            text(x[v], y[v], labels = if1(labels, v), col = if1(label.color, 
                v), family = if1(label.family, v), font = if1(label.font, 
                v), cex = if1(label.cex, v))
        })
    }
    rm(x, y)
    invisible(NULL)
}

igraph.Arrows2=function (x1, y1, x2, y2, code = 2, size = 1, width = 1.2/4/cin, 
    open = TRUE, sh.adj = 0.1, sh.lwd = 1, sh.col = if (is.R()) par("fg") else 1, 
    sh.lty = 1, h.col = sh.col, h.col.bo = sh.col, h.lwd = sh.lwd, 
    h.lty = sh.lty, curved = FALSE) 
{
    cin <- size * par("cin")[2]
	
	lx <- length(x1)
    
    uin <- if (is.R()) 
        1/xyinch()
    else par("uin")
    
    delta <- sqrt(h.lwd) * par("cin")[2] * 0.005
   
    #modify for multiple sizes here
    arrlist=lapply(1:length(size),function(w){
		x <- sqrt(seq(0, cin[w]^2, length = floor(35 * cin[w]) + 2))
    	x.arr <- c(-rev(x), -x)
		return(list(x=x,x.arr=x.arr))
    })
    x=lapply(arrlist,function(w) w$x)
    x.arr=lapply(arrlist,function(w) w$x.arr)
    #pad size to same length as edges
    wx=lx/length(x)
    if(wx>1){
         x=rep(x,ceiling(wx))
         x.arr=rep(x.arr,ceiling(wx))
		 cin=rep(cin,ceiling(wx))
    }
	wx=lx/length(width)
	if(wx>1){
         width=rep(width,ceiling(wx))
    }
	width <- width * (1.2/4/cin)
	
    #modify for multiple widths here
    arrlist=lapply(1:length(width),function(w){

    	wx2<-width[w]*x[[w]]^2
    	y.arr <- c(-rev(wx2 + delta), wx2 + delta)#repeat it backwards
    	deg.arr <- c(atan2(y.arr, x.arr[[w]]), NA)#atan2 of y array and x array
    	r.arr <- c(sqrt(x.arr[[w]]^2 + y.arr^2), NA) #square root of x array and y array
    	return(list(deg.arr=deg.arr,r.arr=r.arr))
    })
    deg.arr=do.call(c,lapply(arrlist,function(w) w$deg.arr))
    r.arr=do.call(c,lapply(arrlist,function(w) w$r.arr))
	deg.arr2=lapply(arrlist,function(w) w$deg.arr)
	
    bx1 <- x1
    bx2 <- x2
    by1 <- y1
    by2 <- y2
    
	#modify for multiple arrow sizes

	if(length(cin)==1){
		r.seg <- rep(cin * sh.adj, lx)
		theta1 <- atan2((y1 - y2) * uin[2], (x1 - x2) * uin[1])
		th.seg1 <- theta1 + rep(atan2(0, -cin), lx)
		theta2 <- atan2((y2 - y1) * uin[2], (x2 - x1) * uin[1])
		th.seg2 <- theta2 + rep(atan2(0, -cin), lx)
	}else{
		r.seg <- cin * sh.adj
		theta1 <- atan2((y1 - y2) * uin[2], (x1 - x2) * uin[1])
		th.seg1 <- theta1 + (atan2(0, -cin))
		theta2 <- atan2((y2 - y1) * uin[2], (x2 - x1) * uin[1])
		th.seg2 <- theta2 + (atan2(0, -cin))		
	}
	
	
    x1d <- y1d <- x2d <- y2d <- 0
    if (code %in% c(1, 3)) {
        x2d <- r.seg * cos(th.seg2)/uin[1]
        y2d <- r.seg * sin(th.seg2)/uin[2]
    }
    if (code %in% c(2, 3)) {
        x1d <- r.seg * cos(th.seg1)/uin[1]
        y1d <- r.seg * sin(th.seg1)/uin[2]
    }
    if (is.logical(curved) && all(!curved) || is.numeric(curved) && 
        all(!curved)) {
        segments(x1 + x1d, y1 + y1d, x2 + x2d, y2 + y2d, lwd = sh.lwd, 
            col = sh.col, lty = sh.lty)
        phi <- atan2(y1 - y2, x1 - x2)
        r <- sqrt((x1 - x2)^2 + (y1 - y2)^2)
        lc.x <- x2 + 2/3 * r * cos(phi)
        lc.y <- y2 + 2/3 * r * sin(phi)
    }
    else {
        if (is.numeric(curved)) {
            lambda <- curved
        }
        else {
            lambda <- as.logical(curved) * 0.5
        }
        lambda <- rep(lambda, length.out = length(x1))
        c.x1 <- x1 + x1d
        c.y1 <- y1 + y1d
        c.x2 <- x2 + x2d
        c.y2 <- y2 + y2d
        midx <- (x1 + x2)/2
        midy <- (y1 + y2)/2
        spx <- midx - lambda * 1/2 * (c.y2 - c.y1)
        spy <- midy + lambda * 1/2 * (c.x2 - c.x1)
        sh.col <- rep(sh.col, length = length(c.x1))
        sh.lty <- rep(sh.lty, length = length(c.x1))
        sh.lwd <- rep(sh.lwd, length = length(c.x1))
        lc.x <- lc.y <- numeric(length(c.x1))
        for (i in seq_len(length(c.x1))) {
            if (lambda[i] == 0) {
                segments(c.x1[i], c.y1[i], c.x2[i], c.y2[i], 
                  lwd = sh.lwd[i], col = sh.col[i], lty = sh.lty[i])
                phi <- atan2(y1[i] - y2[i], x1[i] - x2[i])
                r <- sqrt((x1[i] - x2[i])^2 + (y1[i] - y2[i])^2)
                lc.x[i] <- x2[i] + 2/3 * r * cos(phi)
                lc.y[i] <- y2[i] + 2/3 * r * sin(phi)
            }
            else {
                spl <- xspline(x = c(c.x1[i], spx[i], c.x2[i]), 
                  y = c(c.y1[i], spy[i], c.y2[i]), shape = 1, 
                  draw = FALSE)
                lines(spl, lwd = sh.lwd[i], col = sh.col[i], 
                  lty = sh.lty[i])
                if (code %in% c(2, 3)) {
                  x1[i] <- spl$x[3 * length(spl$x)/4]
                  y1[i] <- spl$y[3 * length(spl$y)/4]
                }
                if (code %in% c(1, 3)) {
                  x2[i] <- spl$x[length(spl$x)/4]
                  y2[i] <- spl$y[length(spl$y)/4]
                }
                lc.x[i] <- spl$x[2/3 * length(spl$x)]
                lc.y[i] <- spl$y[2/3 * length(spl$y)]
            }
        }
    }
    if (code %in% c(2, 3)) {
		theta <- atan2((by2 - y1) * uin[2], (bx2 - x1) * uin[1])
			
		#alter here for multiple arrow widths/size
		if(length(width)==1&length(size)==1){
			Rep <- rep(length(deg.arr), lx)
		} else {
			Rep <- sapply(deg.arr2,length)
		}
        p.x2 <- rep(bx2, Rep)
        p.y2 <- rep(by2, Rep)
		if(length(width)==1&length(size)==1){
       	 ttheta <- rep(theta, Rep) + rep(deg.arr, lx)
		 r.arr <- rep(r.arr, lx) 
		} else {#repping not neccesary
		  ttheta <- rep(theta, Rep) + deg.arr
        }
        if (open) 
            lines((p.x2 + r.arr * cos(ttheta)/uin[1]), (p.y2 + 
                r.arr * sin(ttheta)/uin[2]), lwd = h.lwd, col = h.col.bo, 
                lty = h.lty)
        else polygon(p.x2 + r.arr * cos(ttheta)/uin[1], p.y2 + 
            r.arr * sin(ttheta)/uin[2], col = h.col, lwd = h.lwd, 
            border = h.col.bo, lty = h.lty)
    }
    if (code %in% c(1, 3)) {
        x1 <- bx1
        y1 <- by1
        tmp <- x1
        x1 <- x2
        x2 <- tmp
        tmp <- y1
        y1 <- y2
        y2 <- tmp
        theta <- atan2((y2 - y1) * uin[2], (x2 - x1) * uin[1])
        lx <- length(x1)
        Rep <- rep(length(deg.arr), lx)
        p.x2 <- rep(x2, Rep)
        p.y2 <- rep(y2, Rep)
        ttheta <- rep(theta, Rep) + rep(deg.arr, lx)
        r.arr <- rep(r.arr, lx)
        if (open) 
            lines((p.x2 + r.arr * cos(ttheta)/uin[1]), (p.y2 + 
                r.arr * sin(ttheta)/uin[2]), lwd = h.lwd, col = h.col.bo, 
                lty = h.lty)
        else polygon(p.x2 + r.arr * cos(ttheta)/uin[1], p.y2 + 
            r.arr * sin(ttheta)/uin[2], col = h.col, lwd = h.lwd, 
            border = h.col.bo, lty = h.lty)
    }
    list(lab.x = lc.x, lab.y = lc.y)
}
```

```{r}
environment(plot.igraph2) <- asNamespace('igraph')
environment(igraph.Arrows2) <- asNamespace('igraph')
```

```{r, fig.width=15, fig.height=15}
plot.igraph2(rnet,
             layout = kamadaLayout,
             edge.width=E(rnet)$weight,
             edge.arrow.size=log(E(rnet)$weight),
             edge.arrow.width=log(E(rnet)$weight),
             edge.curved = 0.15,
             vertex.color = "tomato",
             vertex.frame.color = NA,
             vertex.label.font = 2,
             vertex.label.cex = .7,
             vertex.label.color = "black")

```

